### 2021-04-01 Chapter-3/Chapter-3.tex
update

The first type of leakage sites is secret-dependent control-flow leakage sites. Shown in Figure~\ref{fig:chapter3:cf}(a), the

>>>>

If the input sensitive data can affect the control flow of the victim program, then an attacker can infer the sensitive data by observing the control flow during the execution. Figure~\ref{fig:chapter3:cf}(a) shows such an example. The function takes a public value \textsf{m} and a secret \textsf{k} as the input values. The code at line 2 ensures that the lower 7 bits of the value \textsf{k} does not affect the value \textsf{b}. However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site. If the eighth bit of \textsf{m} is 1, then can attacker can also infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6. The right figure shows the corresponding machine code. It has a conditional jump instruction \textsf{jne}. As a result, the sensitive input \textsf{k} can affects the program counter (the rip register), which is the root cause of the side-channel leakages.  Figure~\ref{fig:chapter3:cf}(b) shows an opposite situation. While the sensitive input \textsf{k} can affect the if else branch, the compiler removes the branch with a conditional set instruction.
